Global well-being and mental health in the internet age

### 2022-07-14 Analysis.qmd
Improve tables

#' Custom kableExtra formatting
#'
#' @param a table from kbl()
#'
#' @return a table
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = Font,
    font_size = 13,
    position = "center",
    full_width = FALSE
  )
}
```

@@

# Then display the table
tab %>% 
  filter(Country == "World") %>% 
  # Create a result string for table
  mutate(
    raw_result = str_glue(
      "{number(raw_mean, .001)}
      [{number(raw_low, .001)}, 
      {number(raw_high, .001)}] 
      ({percent2(pd, .1)})"
    ),
    scaled_result = str_glue(
      "{number(scaled_mean, .001)} 
      [{number(scaled_low, .001)}, 
      {number(scaled_high, .001)}] 
      ({percent2(rope, .1)})"
    ),
    # ROPE doesn't make sense for change over time (it is ROPE)
    scaled_result = if_else(Predictor == "Time", "", as.character(scaled_result))
  ) %>% 
  select(
    Predictor, 
    Outcome, 
    `Raw association` = raw_result, 
    `Scaled association` = scaled_result
  ) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  kbl() %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    number = c(
      "Raw associations are percentage changes in outcomes associated with a decade (Time) or 10% (Internet & Mobile) increase in the predictor. Numbers indicate posterior means, [95%CI], and (posterior probability of direction).", 
      "Scaled associations are percentage changes in outcomes associated with per-decade change in the predictor (“decade-equivalent” association). Numbers indicate posterior means, [95%CI], and (posterior probability inside the region of practical equivalence; i.e. probability that the association is smaller than the per-decade change in the respective outcome)."
    )
  )
```

@@

cor_sum <- cor_pars_brm %>% 
  mutate(
    across(
      internet:mobile, 
      ~map(., ~describe_posterior(., centrality = "mean", test = "pd"))
    )
  )
cor_sum %>% 
  pivot_longer(-outcome, names_to = "Predictor") %>% 
  unnest(value) %>% 
  filter(str_detect(Parameter, "cor_")) %>% 
  mutate(
    across(Mean:CI_high, ~number(., .01)), pd = percent2(pd, .1)
  ) %>% 
  transmute(
    Predictor = str_to_title(Predictor),
    Correlation = if_else(
      str_detect(Parameter, "Intercept"), "Intercepts", "Slopes"
    ),
    Outcome = str_replace(outcome, "_", " "),
    Summary = str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})")
  ) %>% 
  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
  arrange(Correlation, Outcome) %>% 
  mutate(
    Correlation = if_else(Outcome == "Life satisfaction", Correlation, "")
  ) %>% 
  kbl() %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    general = "Numbers indicate the correlations [95%CI] between the intercepts and slopes of time of the corresponding outcome and internet / mobile broadband adoption.",
    general_title = "Note. ",
    footnote_as_chunk = TRUE
  )
```

>>>>

#' Custom kableExtra formatting
#'
#' @param a table from kbl()
#'
#' @return a table
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = "Arial",
    font_size = 13,
    position = "center",
    full_width = FALSE
  )
}
```

@@

# Function to align positive and negative values
number2 <- function(x, accuracy = .001, pad = FALSE) {
  out <- number(
    x,
    accuracy = accuracy,
    style_negative = "minus"
    )

  # Justify on decimal point
  if (pad) {
    # Add white space to start of non-negative numbers
    out[str_starts(out, "[0-9]")] <- str_c(
      "<code style='background:white'> </code>", 
      out[str_starts(out, "[0-9]")]
    )
  }
  out

}

# Then display the table
tab %>% 
  filter(Country == "World") %>% 
  # Create a result string for table
  mutate(
    raw_result = str_glue(
      "{number2(raw_mean, pad = TRUE)}
      [{number2(raw_low)}, 
      {number2(raw_high)}] 
      ({percent2(pd)})"
    ),
    scaled_result = str_glue(
      "{number2(scaled_mean, pad = TRUE)} 
      [{number2(scaled_low)}, 
      {number2(scaled_high)}] 
      ({percent2(rope)})"
    ),
    # ROPE doesn't make sense for change over time (it is ROPE)
    scaled_result = if_else(Predictor == "Time", "", as.character(scaled_result))
  ) %>% 
  select(
    Predictor, 
    Outcome, 
    `Raw association` = raw_result, 
    `Scaled association` = scaled_result
  ) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  kable(escape = FALSE) %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    number = c(
      "Raw associations are percentage changes in outcomes associated with a decade (Time) or 10% (Internet & Mobile) increase in the predictor. Numbers indicate posterior means, [95%CI], and (posterior probability of direction).", 
      "Scaled associations are percentage changes in outcomes associated with per-decade change in the predictor (“decade-equivalent” association). Numbers indicate posterior means, [95%CI], and (posterior probability inside the region of practical equivalence; i.e. probability that the association is smaller than the per-decade change in the respective outcome)."
    )
  )
```

@@

cor_sum <- cor_pars_brm %>% 
  mutate(
    across(
      internet:mobile, 
      ~map(., ~describe_posterior(., centrality = "mean", test = "pd"))
    )
  )
cor_sum %>% 
  pivot_longer(-outcome, names_to = "Predictor") %>% 
  unnest(value) %>% 
  filter(str_detect(Parameter, "cor_")) %>% 
  mutate(
    Mean = number2(Mean, .01, pad = TRUE),
    across(CI_low:CI_high, ~number(., .01)), 
    pd = percent2(pd, .1)
  ) %>% 
  transmute(
    Predictor = str_to_title(Predictor),
    Correlation = if_else(
      str_detect(Parameter, "Intercept"), "Intercepts", "Slopes"
    ),
    Outcome = str_replace(outcome, "_", " "),
    Summary = str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})")
  ) %>% 
  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
  arrange(Correlation, Outcome) %>% 
  mutate(
    Correlation = if_else(Outcome == "Life satisfaction", Correlation, "")
  ) %>% 
  kbl(escape = FALSE) %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    general = "Numbers indicate the correlations [95%CI] between the intercepts and slopes of time of the corresponding outcome and internet / mobile broadband adoption.",
    general_title = "Note. ",
    footnote_as_chunk = TRUE
  )
```
